\documentclass[12pt]{article}
\usepackage{setspace,hyperref,amsmath,amsfonts,multirow,xcolor}
\usepackage[top=0.5in, bottom=1in, left=1.75in, right=1in, marginparwidth=1.4in]{geometry}
\setlength{\parindent}{-1.55ex}
\usepackage{libertine}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo} % old serif font
\definecolor{lg}{gray}{0.5} % light-gray definition
\definecolor{mg}{gray}{0.3} % light-gray definition
\definecolor{dg}{gray}{0.0} % dark-gray definition
\color{dg}
\renewcommand{\section}[1]{\pagebreak[3]%
    \llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright {\color{lg}#1}}}}%
    \vspace{-\baselineskip}\par}
\newcommand{\topic}[1]{\pagebreak[3]\indent {\color{lg}{\footnotesize #1 }}\\}
\newcommand{\entry}[1]{\indent {\color{lg}\guillemotright}\hspace{2pt}#1\vspace{.25em}\\}
\newcommand{\subentry}[1]{{\color{lg}-} #1\vspace{.25em}\\}
\hypersetup{
    bookmarks=false,        % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Curriculum Vitae},    % title
    pdfauthor={Thomas J. Leeper},     % author
    pdfsubject={Curriculum Vitae},   % subject of the document
    pdfkeywords={Thomas J. Leeper} {Leeper} {CV} {resume} {research}, % list of keywords
    pdfnewwindow=true,      % links in new window
    pdfborder={0 0 0}
}

\begin{document}
{\LARGE Thomas J. Leeper}\\

\today\\

\begin{minipage}[b]{0.5\linewidth}
Department of Government\\
London School of Economics\\
Connaught House 3.21\\
Houghton Street\\
London WC2A 2AE, UK\\
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
Voicemail (USA): +1 651 230 7007\\
Email: \href{mailto:thosjleeper@gmail.com}{thosjleeper@gmail.com}\\
Web: \href{http://www.thomasleeper.com/}{http://www.thomasleeper.com/}\\
\end{minipage}

\section{Education}
\entry{PhD, Political Science, Northwestern University (2012)}
%\subentry{Dissertation: {\em Essays on Political Information and the Dynamics of Public Opinion}}
%\subentry{Chair: Jamie Druckman}
%\subentry{Committee: Benjamin Page, Dennis Chong, \& Fay Lomax Cook}
%\subentry{Fields: American Politics (major) and Methodology (minor)}
%\entry{Summer Institute in Political Psychology, Stanford University (2009)}
%\subentry{NU Law School Workshops on Causal Inference (2010) and Bayesian Inference (2011)}
\entry{M.A., Northwestern University (2010)}
%\subentry{Masters Thesis: ``Revisiting Political Awareness: Has Public Opinion Research Forsaken Federalism?'' Committee: Drs. James N. Druckman (Chair) and Dennis Chong.}
\entry{B.A. {\em magna cum laude} with Distinction, Political Science \& Global Studies, University of Minnesota---Twin Cities (2007)}
%\subentry{Political Science Concentration: Political Psychology, Beliefs, \& Behavior}
%\subentry{Minors: Spanish Studies and Learning Abroad}
%\subentry{Semester Abroad: Fundación Jose Ortega y Gassett, Toledo, Castilla-La Mancha, Spain (2006)}
%\subentry{Honors Thesis, magna cum laude: ``Sympathy, Dissonance, and Affect Transfer: The Electoral Implications of Political Death.'' Adviser: Dr. Joanne Miller.}

\section{Academic Appointments}
\entry{Department of Government, London School of Economics and Political Science}
	\subentry{Associate Professor in Political Behaviour (2017--Present)}
	\subentry{Assistant Professor in Political Behaviour (2015--2017)}
\entry{Department of Political Science, Aarhus University}
	\subentry{Postdoc (2013--2015)}

%\section{Publications}
\section{Selected\\Peer-Reviewed\\Publications}
%\topic{Peer-Reviewed Publications}
    \entry{Thomas J. Leeper. 2017. ``Am I a Methodologist? Asking for a Friend.'' \textit{PS: Political Science \& Politics}: In press.}
	\entry{Joshua Robison, Thomas J. Leeper, and James N. Druckman. ``Do Heterogeneous Social Networks Undermine Attitude Strength?'' \textit{Political Psychology}. \href{http://doi.org/10.1111/pops.12374}{doi:10.1111/pops.12374}}
    \entry{Thomas J. Leeper. 2017. ``How Does Treatment Self-Selection Affect Inferences About Political Communication?'' \textit{Journal of Experimental Political Science} 4(1): 21--33. \href{http://doi.org/10.1017/XPS.2017.1}{doi:10.1017/XPS.2017.1}}
	\entry{Thomas J. Leeper. 2016. ``Crowdsourced Data Preprocessing with R and Amazon Mechanical Turk.'' \textit{R Journal} 8(1): 276--288. \href{https://journal.r-project.org/archive/2016-1/leeper.pdf}{https://journal.r-project.org/archive/2016-1/leeper.pdf}}
	\entry{Kevin J. Mullinix, Thomas J. Leeper, James N. Druckman, and Jeremy Freese. 2015. ``The Generalizability of Survey Experiments.'' \textit{Journal of Experimental Political Science} 2(2): 109--138. \href{http://doi.org/10.1017/XPS.2015.19}{doi:10.1017/XPS.2015.19}}
		%\subentry{Media coverage at \href{https://www.washingtonpost.com/news/monkey-cage/wp/2016/03/09/does-social-science-have-a-replication-crisis/}{The Monkey Cage}}
	\entry{Thomas J. Leeper. 2014. ``Cognitive Style and the Survey Response.'' \textit{Public Opinion Quarterly} 78(4): 974--983. \href{http://doi.org/10.1093/poq/nfu042}{doi:10.1093/poq/nfu042}}
	\entry{Thomas J. Leeper. 2014. ``The Informational Basis for Mass Polarization.'' \textit{Public Opinion Quarterly} 78(1): 27--46. \href{http://doi.org/10.1093/poq/nft045}{doi:10.1093/poq/nft045}}
	\entry{Thomas J. Leeper, and Rune Slothuus. 2014. ``Political Parties, Motivated Reasoning, and Public Opinion Formation.'' \textit{Advances in Political Psychology} 35 (Supplement 1): 129--156. \href{http://doi.org/10.1111/pops.12164}{doi:10.1111/pops.12164}}
	%\entry{Toby Bolsen, Thomas J. Leeper, and Matthew Shapiro. 2014. ``Doing What Others Do: Norms, Science, and Collective Action on Global Warming.'' \textit{American Politics Research} 42(1): 65--89. \href{http://doi.org/10.1177/1532673X13484173}{doi:10.1177/1532673X13484173}}
	\entry{Toby Bolsen, and Thomas J. Leeper. 2013. ``Self-Interest and Attention to News among Issue Publics.'' \textit{Political Communication} 30(3): 329--348.\\ \href{http://doi.org/10.1080/10584609.2012.737428}{doi:10.1080/10584609.2012.737428}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Learning More from Political Communication Experiments: Pretreatment and Its Effects.'' \textit{American Journal of Political Science} 56(4): 875--896. \href{http://doi.org/10.1111/j.1540-5907.2012.00582.x}{doi:10.1111/j.1540-5907.2012.00582.x}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Is Public Opinion Stable? Resolving the Micro-Macro Disconnect in Studies of Public Opinion.'' \textit{Daedalus} 141(4): 50--68. \href{http://doi.org/10.1162/DAED\_a\_00173}{doi:10.1162/DAED\_a\_00173}}
	\entry{James N. Druckman, Jordan Fein, and Thomas J. Leeper. 2012. ``A Source of Bias in Public Opinion Stability.'' \textit{American Political Science Review} 106(2): 430--454.\\ \href{http://doi.org/10.1017/S0003055412000123}{doi:10.1017/S0003055412000123}}

%\topic{Other Publications}
%\entry{Thomas J. Leeper. ``The Multiple Paths to Credibility.'' {\em The Political Methodologist}: In press.}
%\entry{James N. Druckman, Thomas J. Leeper, and Kevin J. Mullinix. 2014. ``The Experimental Study of Legislative Behaviors.'' In Thomas Saalfeld, and Kaare Str\o m, eds., {\em The Oxford Handbook of Legislative Studies}, 194--210. Oxford, UK: Oxford University Press.}
%\entry{Thomas J. Leeper. 2014. ``Making High-Resolution Graphics for Academic Publishing.'' {\em The Political Methodologist} 21(1): 2--5.}
%\entry{Thomas J. Leeper. 2013. ``Crowdsourcing with R and the MTurk API.'' {\em The Political Methodologist} 2(2): 2--7.}
%\entry{Thomas J. Leeper. 2011. ``The Role of Protocol in the Design and Reporting of Experiments.'' {\em The Experimental Political Scientist} 2(1): 6-10.}%
%\entry{Marybeth Neal, Thomas J. Leeper, and Susan Root. 2009. ``Attributes of Quality Service-Learning: Findings from the Transitioning to Adulthood Survey.'' In James C. Kielsmeier, Susan Root, Bjorn Lyngstad, and Caryn Pernu, eds., {\em Growing to Greatness 2009}. St. Paul: NYLC.}

\clearpage

\section{Grants\\and\\Funding}
\entry{ESRC Research Grant (ES/R000573/1) (2017), \textsterling120,025, with Sara Hobolt and James Tilley}
\entry{LSE STICERD Small Grant, \textsterling 4,920 (2017), with Sara Hobolt}
\entry{LSE Research Infrastructure and Investment Fund, \textsterling 11,611 (approx. \$17,000, 2016)}
\entry{Named project member on Danish Council for Independent Research Sapere Aude grant to Rune Slothuus, total award 7,050,249 DKK (approx. \textsterling 690,000) (2014)}
\entry{Time-Sharing Experiments for the Social Sciences, approx. \$12,000 (2013)}
\entry{National Science Foundation Doctoral Dissertation Improvement Grant, \$12,000 (2012)}
\entry{Northwestern Career Development Grant for Social Scientists, \$400 (2012)}
\entry{Northwestern University TGS Conference Travel Grant, \$500 (2012)}
\entry{APSA Annual Meeting Travel Grant, \$200 (2011)}
\entry{Northwestern University TGS Conference Travel Grant, \$700 (2011)}
\entry{Weinberg College of Arts and Sciences Humanities and Social Sciences Technology-Enhanced Doctoral Research Award, \$600 (2011)}
\entry{Northwestern University Graduate Research Grant, \$3,000 (2011)}
\entry{Northwestern University MacArthur Fund grant, \$2,000 (2009)}
%\entry{Northwestern University Fellowship, \$20,000 (2008-2009, 2012-2013)}
%\entry{Bush Foundation Study Abroad Scholarship, University of Minnesota, \$750 (2006)}
%\entry{Hearst Foundation United States Senate Youth Program Scholarship, \$5,000 (2005)}

\section{Honors\\and\\Awards}
\entry{Best Paper Award from APSA Elections, Public OpInion, and Voting Behavior Section, with Rune Slothuus (2017)}
\entry{LSE Promotions Committee Teaching Prize (2017)}
\entry{Best Paper Award from APSA Experimental Research Section, with Kevin J. Mullinix (2015)}
\entry{APSA Political Psychology Section Distinguished Junior Scholars Award (2014)}
\entry{Best Paper Award from APSA Elections, Public Opinion, and Voting Behavior Section (2012)}
\entry{Timothy Cook Best Graduate Student Paper Award from APSA Political Communication Section (2012)}
\entry{Honorable Mention, National Science Foundation Graduate Research Fellowship (2009)}
%\entry{Early election, Phi Beta Kappa, University of Minnesota (2007)}
%\entry{College of Liberal Arts Undergraduate Honors Program, University of Minnesota (2006-2007)}
%\entry{College of Liberal Arts Dean's List, University of Minnesota (2005-2007)}
%\entry{Minnesota Delegate, United States Senate Youth Program (2005)}

%\section{Software Development}
%\entry{Principal or contributing developer for R packages: \href{https://github.com/leeper/arco}{arco}, \href{https://cran.r-project.org/package=colourlovers}{colourlovers}, \href{https://github.com/hrbrmstr/dtupdate}{dtupdate}, \href{https://cran.r-project.org/package=dvn}{dvn}, \href{https://github.com/rOpenGov/federalregister}{federalregister}, \href{https://github.com/leeper/ghit}{ghit}, \href{https://cran.r-project.org/package=imguR}{imguR}, \href{https://github.com/leeper/margins}{margins}, \href{https://github.com/leeper/meme}{meme}, \href{https://github.com/leeper/microworkers}{microworkers}, \href{https://github.com/rOpenGov/mpg}{mpg}, \href{https://cran.r-project.org/package=MTurkR}{MTurkR}, \href{https://github.com/ropenhealth/openfda}{openfda}, \href{https://cran.r-project.org/package=pollstR}{pollstR}, \href{https://github.com/rOpenGov/recalls}{recalls}, \href{https://cran.r-project.org/package=rio}{rio}, \href{https://cran.r-project.org/package=rite}{CRAN}, \href{https://cran.r-project.org/package=Rmonkey}{Rmonkey}, \href{https://github.com/rOpenGov/RPublica}{RPublica}, \href{https://github.com/leeper/rscribd}{rscribd}, \href{https://cran.r-project.org/package=rsunlight}{rsunlight}, \href{https://github.com/leeper/slopegraph}{slopegraph}, \href{https://cran.r-project.org/package=sparktex}{sparktex}, \href{https://cran.r-project.org/package=UNF}{UNF}, \href{https://github.com/rOpenGov/usbroadband}{usbroadband}, \href{https://cran.r-project.org/package=webuse}{webuse}, and various packages contributed to the cloudyr project.}


\section{Service}
\topic{Editing}
	\entry{Editorial Board, \href{http://www.tandfonline.com/toc/upcp20/current}{\textit{Political Communication}} (2017--2020)}
    \entry{Editorial Board, \href{http://joss.theoj.org/}{\textit{Journal of Open Source Software}} (2017--)}
    \entry{Editorial Board, \href{http://link.springer.com/journal/11109}{\textit{Political Behavior}} (2016--2019)}
	\entry{Editorial Board, \href{http://riojournal.com/}{\textit{Research Ideas and Outcomes}} (2015--)}
	\entry{Associate PI, Time-Sharing Experiments for the Social Sciences (2013--)}

\topic{Peer Review Activity}
	\entry{Journal Reviewer (see \href{https://publons.com/a/634082/}{Publons Profile}):\\\textit{American Journal of Political Science}, \textit{American Political Science Review}, \textit{American Politics Research}, \textit{British Journal of Political Science}, \textit{Comparative Political Studies}, \textit{DATABASE: The Journal of Biological Databases and Curation}, \textit{European Union Politics}, \textit{Field Methods}, \textit{Future Internet}, \textit{International Journal of Public Opinion Research}, \textit{Irish Political Studies}, \textit{Japanese Journal of Political Science}, \textit{Journal of Communication}, \textit{Journal of Elections, Public Opinion, and Parties}, \textit{Journal of Ethnic and Migration Studies}, \textit{Journal of Experimental Political Science}, \textit{Journal of Politics}, \textit{Journal of Public Policy}, \textit{Journal of Women, Politics \& Policy}, \textit{Journalism \& Mass Communication Quarterly}, \textit{Nature Climate Change}, \textit{PLoS One}, \textit{Political Analysis}, \textit{Political Behavior}, \textit{Political Communication}, \textit{Political Psychology}, \textit{Political Research Quarterly}, \textit{Political Science Research and Methods}, \textit{Politics, Groups, and Identities}, \textit{PS: Political Science \& Politics}, \textit{Public Administration}, \textit{Public Opinion Quarterly}, \textit{Quarterly Journal of Political Science}, \textit{Research \& Politics}, \textit{R Journal}, \textit{SAGE Open}, \textit{Scandinavian Political Studies}, \textit{Science}, \textit{Social Science Computer Review}}
	\entry{Funding Reviewer: Israeli Science Foundation, Netherlands Organisation for Scientific Research, U.K. Economic and Social Research Council, U.S. National Science Foundation}
	\entry{Book Reviewer: Cambridge University Press, MIT Press, Princeton University Press, Routledge Press, SAGE Publications}
	\entry{Other Peer Review Activity:\\ AAPOR Annual Conference, Center for Experimental Social Science at Nuffield College--Oxford, rOpenSci R Package Onboarding, TESS: Time-Sharing Experiments for the Social Sciences}

\end{document}
