\documentclass[12pt]{article}
\usepackage{setspace,hyperref,amsmath,amsfonts,multirow,xcolor}
\usepackage[top=1in, bottom=1in, left=1.75in, right=1in, marginparwidth=1.4in]{geometry}
\setlength{\parindent}{-1.55ex}
\usepackage{libertine}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo} % old serif font
\definecolor{lg}{gray}{0.5} % light-gray definition
\definecolor{mg}{gray}{0.3} % light-gray definition
\definecolor{dg}{gray}{0.0} % dark-gray definition
\color{dg}
\renewcommand{\section}[1]{\pagebreak[3]%
    \llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright {\color{lg}#1}}}}%
    \vspace{-\baselineskip}\par}
\newcommand{\topic}[1]{\pagebreak[3]\indent {\color{lg}{\footnotesize #1 }}\\}
\newcommand{\entry}[1]{\indent {\color{lg}\guillemotright}\hspace{2pt}#1\vspace{.25em}\\}
\newcommand{\subentry}[1]{{\color{lg}-} #1\vspace{.25em}\\}
\hypersetup{
    bookmarks=false,        % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Curriculum Vitae},    % title
    pdfauthor={Thomas J. Leeper},     % author
    pdfsubject={Curriculum Vitae},   % subject of the document
    pdfkeywords={Thomas J. Leeper} {Leeper} {CV} {resume} {research}, % list of keywords
    pdfnewwindow=true,      % links in new window
    pdfborder={0 0 0}
}

\begin{document}
{\LARGE Thomas J. Leeper}\\

\today\\

\begin{minipage}[b]{0.5\linewidth}
Department of Government\\
London School of Economics\\
Connaught House 3.21\\
Houghton Street\\
London WC2A 2AE, UK
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
Office Phone (UK): +44 (0)20 7955 7191\\
Voicemail (USA): +1 651 230 7007\\
Email: \href{mailto:thosjleeper@gmail.com}{thosjleeper@gmail.com}\\
Web: \href{http://www.thomasleeper.com/}{http://www.thomasleeper.com/}\\
ORCID: \href{http://orcid.org/0000-0003-4097-6326}{0000-0003-4097-6326}
\end{minipage}\\

\section{Education}
\entry{PhD, Political Science, Northwestern University (2012)}
\subentry{Dissertation: {\em Essays on Political Information and the Dynamics of Public Opinion}}
%\subentry{Chair: Jamie Druckman}
%\subentry{Committee: Benjamin Page, Dennis Chong, \& Fay Lomax Cook}
%\subentry{Fields: American Politics (major) and Methodology (minor)}
\entry{Summer Institute in Political Psychology, Stanford University (2009)}
%\subentry{NU Law School Workshops on Causal Inference (2010) and Bayesian Inference (2011)}
\entry{M.A., Northwestern University (2010)}
%\subentry{Masters Thesis: ``Revisiting Political Awareness: Has Public Opinion Research Forsaken Federalism?'' Committee: Drs. James N. Druckman (Chair) and Dennis Chong.}
\entry{B.A. {\em magna cum laude} with Distinction, Political Science \& Global Studies, University of Minnesota---Twin Cities (2007)}
%\subentry{Political Science Concentration: Political Psychology, Beliefs, \& Behavior}
%\subentry{Minors: Spanish Studies and Learning Abroad}
%\subentry{Semester Abroad: Fundación Jose Ortega y Gassett, Toledo, Castilla-La Mancha, Spain (2006)}
%\subentry{Honors Thesis, magna cum laude: ``Sympathy, Dissonance, and Affect Transfer: The Electoral Implications of Political Death.'' Adviser: Dr. Joanne Miller.}

\section{Academic Appointments}
\entry{Facebook}
	\subentry{Research Scientist, Core Data Science (2018--)}
\entry{Methodology Department, London School of Economics and Political Science}
	\subentry{Senior Visiting Fellow (2018--)}
\entry{Department of Government, London School of Economics and Political Science}
	\subentry{Associate Professor in Political Behaviour (2017--2018)}
	\subentry{Assistant Professor in Political Behaviour (2015--2017)}
\entry{Department of Political Science, Aarhus University}
	\subentry{Postdoc (2013--2015)}
\entry{Institute for Policy Research, Northwestern University}
	\subentry{Graduate Fellow (2009-2012)}

\section{Publications}
\topic{Peer-Reviewed Publications}
	\entry{Thomas J. Leeper, and Emily Thorson. ``Should We Worry About Sponsorship-Induced Bias in Online Political Science Surveys?'' \textit{Journal of Experimental Political Science}: In press.}
    \entry{Thomas J. Leeper. ``Where Have All the Respondents Gone? Perhaps We Ate Them All.'' \textit{Public Opinion Quarterly}: In press.}
    \entry{Alexander Coppock, Thomas J. Leeper, and Kevin J. Mullinix. ``Generalizability of Heterogeneous Treatment Effect Estimates Across Samples.'' \textit{Proceeding of the National Academy of Sciences}: In press.\\ \href{https://doi.org/10.1073/pnas.1808083115}{doi:10.1073/pnas.1808083115}}
	\entry{Thomas J. Leeper, and Joshua Robison. ``More Important, but for What Exactly? The Insignificant Role of Subjective Issue Importance in Vote Decisions.'' \textit{Political Behavior}: In press.\\ \href{https://doi.org/10.1007/s11109-018-9494-0}{doi:10.1007/s11109-018-9494-0}}
    \entry{Thomas J. Leeper. 2018. ``Am I a Methodologist? Asking for a Friend.'' \textit{PS: Political Science \& Politics} 51(3): 602--606.\\ \href{https://doi.org/10.1017/S1049096518000549}{doi:10.1017/S1049096518000549}}
	\entry{Joshua Robison, Thomas J. Leeper, and James N. Druckman. 2018. ``Do Heterogeneous Social Networks Undermine Attitude Strength?'' \textit{Political Psychology} 39(2): 479--94.\\ \href{http://doi.org/10.1111/pops.12374}{doi:10.1111/pops.12374}}
	\entry{Thomas J. Leeper. 2017. ``How Does Treatment Self-Selection Affect Inferences About Political Communication?'' \textit{Journal of Experimental Political Science} 4(1): 21--33.\\ \href{http://doi.org/10.1017/XPS.2017.1}{doi:10.1017/XPS.2017.1}}
	\entry{Thomas J. Leeper. 2016. ``Crowdsourced Data Preprocessing with R and Amazon Mechanical Turk.'' \textit{R Journal} 8(1): 276--288. \href{https://journal.r-project.org/archive/2016-1/leeper.pdf}{https://journal.r-project.org/archive/2016-1/leeper.pdf}}
	\entry{Kevin J. Mullinix, Thomas J. Leeper, James N. Druckman, and Jeremy Freese. 2015. ``The Generalizability of Survey Experiments.'' \textit{Journal of Experimental Political Science} 2(2): 109--138. \href{http://dx.doi.org/10.1017/XPS.2015.19}{10.1017/XPS.2015.19}}
	\entry{Thomas J. Leeper. 2014. ``Cognitive Style and the Survey Response.'' {\em Public Opinion Quarterly} 78(4): 974--983. \href{http://dx.doi.org/10.1093/poq/nfu042}{doi:10.1093/poq/nfu042}}
	\entry{Thomas J. Leeper. 2014. ``Archiving Reproducible Research with R and Dataverse.'' {\em The R Journal} 6(1): 151--158. \href{http://journal.r-project.org/archive/2014-1/leeper.pdf}{http://journal.r-project.org/archive/2014-1/leeper.pdf}.}
	\entry{Thomas J. Leeper. 2014. ``The Informational Basis for Mass Polarization.'' {\em Public Opinion Quarterly} 78(1): 27--46. \href{http://dx.doi.org/10.1093/poq/nft045}{doi:10.1093/poq/nft045}}
	\entry{Thomas J. Leeper, and Rune Slothuus. 2014. ``Political Parties, Motivated Reasoning, and Public Opinion Formation.'' {\em Advances in Political Psychology} 35 (Supplement 1): 129--156. \href{http://dx.doi.org/10.1111/pops.12164}{doi:10.1111/pops.12164}}
	\entry{Toby Bolsen, Thomas J. Leeper, and Matthew Shapiro. 2014. ``Doing What Others Do: Norms, Science, and Collective Action on Global Warming.'' {\em American Politics Research} 42(1): 65--89. \href{http://dx.doi.org/10.1177/1532673X13484173}{doi:10.1177/1532673X13484173}}
	\entry{Toby Bolsen, and Thomas J. Leeper. 2013. ``Self-Interest and Attention to News among Issue Publics.'' {\em Political Communication} 30(3): 329--348.\\ \href{http://dx.doi.org/10.1080/10584609.2012.737428}{doi:10.1080/10584609.2012.737428}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Learning More from Political Communication Experiments: Pretreatment and Its Effects.'' {\em American Journal of Political Science} 56(4): 875--896. \href{http://dx.doi.org/10.1111/j.1540-5907.2012.00582.x}{doi:10.1111/j.1540-5907.2012.00582.x}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Is Public Opinion Stable? Resolving the Micro-Macro Disconnect in Studies of Public Opinion.'' {\em Daedalus} 141(4): 50--68. \href{http://dx.doi.org/10.1162/DAED\_a\_00173}{doi:10.1162/DAED\_a\_00173}}
	\entry{James N. Druckman, Jordan Fein, and Thomas J. Leeper. 2012. ``A Source of Bias in Public Opinion Stability.'' {\em American Political Science Review} 106(2): 430--454.\\ \href{http://dx.doi.org/10.1017/S0003055412000123}{doi:10.1017/S0003055412000123}}

\topic{Other Publications}
	\entry{Thomas J. Leeper, and Rune Slothuus. ``Deliberation and Framing.'' In Andre B{\"a}chtiger, John Dryzek, Jane Mansbridge, and Mark Warren, eds., \textit{The Oxford Handbook of Deliberative Democracy}. In press.}
	\entry{Thomas J. Leeper. ``The Multiple Routes to Credibility.'' \textit{The Political Methodologist} 23(1): 11--16.\\ Available from: \href{https://thepoliticalmethodologist.files.wordpress.com/2016/02/tpm_v23_n1.pdf}{PDF}, \href{https://thepoliticalmethodologist.com/2015/12/21/the-multiple-routes-to-credibility/}{Blog format}.}
	\entry{James N. Druckman, Thomas J. Leeper, and Kevin J. Mullinix. 2014. ``The Experimental Study of Legislative Behaviors.'' In Thomas Saalfeld, and Kaare Str\o m, eds., {\em The Oxford Handbook of Legislative Studies}, 194--210. Oxford, UK: Oxford University Press.}
	\entry{Thomas J. Leeper. 2014. ``Making High-Resolution Graphics for Academic Publishing.'' {\em The Political Methodologist} 21(1): 2--5.}
	\entry{Thomas J. Leeper. 2013. ``Crowdsourcing with R and the MTurk API.'' {\em The Political Methodologist} 2(2): 2--7.}
	\entry{Thomas J. Leeper. 2011. ``The Role of Protocol in the Design and Reporting of Experiments.'' {\em The Experimental Political Scientist} 2(1): 6-10.}%
	%\entry{Marybeth Neal, Thomas J. Leeper, and Susan Root. 2009. ``Attributes of Quality Service-Learning: Findings from the Transitioning to Adulthood Survey.'' In James C. Kielsmeier, Susan Root, Bjorn Lyngstad, and Caryn Pernu, eds., {\em Growing to Greatness 2009}. St. Paul: NYLC.}


\section{Grants\\and\\Funding}
\entry{R Consortium Infrastructure Steering Committee Grant for RL10N Project, \$10,000 (2016)}
\entry{LSE Research Infrastructure and Investment Fund, \textsterling 11,611 (approx. \$17,000, 2016)}
\entry{Named project member on Danish Council for Independent Research Sapere Aude grant to Rune Slothuus, total award 7,050,249 DKK (approx. \$1,274,748) (2014)}
\entry{Time-Sharing Experiments for the Social Sciences, approx. \$12,000 (2013)}
\entry{National Science Foundation Doctoral Dissertation Improvement Grant, \$12,000 (2012)}
\entry{Northwestern Career Development Grant for Humanists and Social Scientists, \$400 (2012)}
\entry{Northwestern University TGS Conference Travel Grant, \$500 (2012)}
\entry{APSA Annual Meeting Travel Grant, \$200 (2011)}
\entry{Northwestern University TGS Conference Travel Grant, \$700 (2011)}
\entry{Weinberg College of Arts and Sciences Humanities and Social Sciences Technology-Enhanced Doctoral Research Award, \$600 (2011)}
\entry{Northwestern University Graduate Research Grant, \$3,000 (2011)}
\entry{Northwestern University MacArthur Fund grant, \$2,000 (2009)}
%\entry{Northwestern University Fellowship, \$20,000 (2008-2009, 2012-2013)}
%\entry{Bush Foundation Study Abroad Scholarship, University of Minnesota, \$750 (2006)}
%\entry{Hearst Foundation United States Senate Youth Program Scholarship, \$5,000 (2005)}

\section{Honors\\and\\Awards}
\entry{Best Paper Award from APSA Experimental Research Section, with Kevin J. Mullinix (2015)}
\entry{APSA Political Psychology Section Distinguished Junior Scholars Award (2014)}
\entry{Best Paper Award from APSA Elections, Public Opinion, and Voting Behavior Section (2012)}
\entry{Timothy Cook Best Graduate Student Paper Award from APSA Political Communication Section (2012)}
\entry{Honorable Mention, National Science Foundation Graduate Research Fellowship (2009)}
\entry{Early election, Phi Beta Kappa, University of Minnesota (2007)}
\entry{College of Liberal Arts Undergraduate Honors Program, University of Minnesota (2006-2007)}
\entry{College of Liberal Arts Dean's List, University of Minnesota (2005-2007)}
\entry{Minnesota Delegate, United States Senate Youth Program (2005)}

\section{Conference\\Papers\\and\\Invited\\Presentations}
\topic{Conference Papers}
\entry{American Political Science Association Annual Meeting: 2016, 2015, 2014, 2013, 2012, 2011}
\entry{APSA Pre-Conference on Political Communication: 2015}
\entry{Midwest Political Science Association Annual Meeting: 2015, 2014, 2012, 2011, 2010}
\entry{International Society for Political Psychology Annual Meeting: 2016, 2014, 2012}
\entry{American Association for Public Opinion Research Annual Meeting: 2013}
\entry{Danish Political Science Association Annual Meeting: 2014, 2013}
\entry{The useR! Conference: 2015}

\topic{Invited Presentations}
\entry{National Research University Higher School of Economics (2016), The Ohio State University (2016), Universitat Pompeu Fabra (2016), Institute for Advanced Study-Toulouse (2016), European University Institute (2015), Nuffield College, Oxford (2015), Louisiana State University (2014), McGill University (2014), London School of Economics (2014), Aarhus University (2014), Copenhagen University (2014), University of Southern Denmark (2013), Northwestern University (2012), University of Chicago (2011)}


\section{Teaching and Advising}
\topic{Experience: London School of Economics and Political Science}
\entry{Instructor, {\em Public Opinion, Political Psychology, and Citizenship} (Master), LSE, 2016}
\entry{Instructor, {\em Research Design in Political Science} (Bachelor), LSE, 2015--2016}
\topic{Experience: Aarhus University}
\entry{Co-Instructor, {\em Quantitative Political Analysis} (Master/PhD), Aarhus University, 2015}
\entry{Instructor, {\em Surveys for Research and Evaluation} (Master), Aarhus University, 2014}
\entry{Instructor, {\em Issues in American Politics and Government} (Master), Aarhus University, 2014}
\entry{Instructor, {\em Experimentation and Causal Inference} (Master), Aarhus University, 2014}
\entry{Co-Instructor, {\em Quantitative Political Analysis} (Master/PhD), Aarhus University, 2014}
\entry{Instructor, {\em Does Public Opinion Matter?} (Master), Aarhus University, 2013}
%\topic{Experience: Northwestern University}
%\entry{Teaching Assistant, {\em Statistical Research Methods} (Bachelor), Northwestern University, 2011} % Jason Seawright
%\entry{Teaching Assistant, {\em Methods of Political Inference} (Bachelor), Northwestern University, 2011} % Jim Mahoney
%\entry{Teaching Assistant, {\em Political Psychology of Mass Behavior} (Bachelor), University of Minnesota, 2007} % Chris Galdieri

\topic{Pedagogical Training}
\entry{Postgraduate Certificate in Higher Education, London School of Economics and Political Science, 2015--2016}
\entry{Various Academic Development Programme workshops, London School of Economics and Political Science, 2015--Present}
\entry{Educational IT -- Go Online, Aarhus University, 2013}
\entry{Teaching Training Programme for Assistant Professors and Postdocs, Aarhus University, 2013}
\entry{New Teaching Assistant Conference, Northwestern University, 2010}

\section{Service}
\topic{Institutional (London School of Economics and Political Science)}
	\entry{Member, Research Ethics Committee (2016--2019)}
	\entry{Participant and presenter, Teaching and Learning Centre Research Methods Teaching Practice and Exchange Forum (2015--)}
\topic{Departmental (London School of Economics and Political Science)}
	\entry{Organizer, Political Behaviour Seminar (2016--)}
	\entry{Departmental Presenter, LSE Open Day (2016)}
	\entry{Search committee, EUDEMOS project Postdoc (2016)}
	\entry{Faculty Participant, Government Department Townhall (2015--)}

\topic{Disciplinary}
	\entry{Editorial Board, \href{http://riojournal.com/}{{\em Research Ideas and Outcomes}} (2015--)}
	\entry{Associate PI, Time-Sharing Experiments for the Social Sciences (2013--)}
	\entry{Journal Reviewer for 33 journals, including:\\\textit{American Journal of Political Science}, \textit{American Political Science Review}, \textit{British Journal of Political Science}, \textit{Comparative Political Studies}, \textit{International Journal of Public Opinion Research}, \textit{Journal of Communication}, \textit{Journal of Elections, Public Opinion, and Parties}, \textit{Journal of Experimental Political Science}, \textit{Journal of Politics}, \textit{Journalism \& Mass Communication Quarterly}, \textit{PLoS One}, \textit{Political Analysis}, \textit{Political Behavior}, \textit{Political Communication}, \textit{Political Psychology}, \textit{Political Science Research and Methods}, \textit{Public Opinion Quarterly}, \textit{Quarterly Journal of Political Science}, \textit{Research \& Politics}, \textit{R Journal}, \textit{Science}}
	\entry{Funding Reviewer: Israeli Science Foundation, U.K. Economic and Social Research Council, U.S. National Science Foundation}
	\entry{Book Reviewer: MIT Press, Routledge Press, SAGE Publications}
	\entry{Other Peer Review Activity:\\ AAPOR Annual Conference, Center for Experimental Social Science at Nuffield College--Oxford, rOpenSci R Package Onboarding, TESS: Time-Sharing Experiments for the Social Sciences}
	\entry{Panel Discussant: AAPOR (2013), APSA (2012, 2014, 2015, 2016), DPSA (2013, 2014), ISPP (2012), MPSA (2014, 2015)}
	\entry{Panel Chair: APSA (2013), ISPP (2013, 2014), MPSA (2014, 2015)}
	\entry{Roundtable participant: MPSA (2015)}
	\entry{Panel Organizer: APSA (2013): ``Advances in Experiments on Media and Information Choices''}
	\entry{Committees and Other Service:}
	\subentry{Committee member, APSA Political Psychology Career Achievement Award (2015)}
	\subentry{Committee member, APSA Pol.Comm. Section Doris Graber Book Award (2014)}
	\subentry{Committee member, APSA Political Psychology Section Best Paper Award (2014)}
	\subentry{Section Chair, Experimental Research Section, MPSA (2014)}
	\subentry{Associate PI, Time-Sharing Experiments for the Social Sciences (2013--)}
	\entry{Memberships: APSA (2007--), MPSA (2009--), AAPOR (2009--), ISPP (2009--)}

\topic{Public Engagement}
\entry{Open Science Evangelism}
	\subentry{Principal or contributing developer for more than 50 packages for the R language.}
	\subentry{Co-Founder, \href{http://rl10n.github.io/}{RL10N: An R Localization Project} (2016-) with Richard Cotton}
	\subentry{Founder, \href{http://cloudyr.github.io/}{the cloudyr project} (2014-)}
	\subentry{Contributing developer, \href{http://ropensci.org/}{rOpenHealth} (2015-); \href{http://ropensci.org/}{rOpenSci} (2014-); \href{http://ropengov.github.io/}{rOpenGov} (2014-)}
	\subentry{Co-maintainer, R Task Views:  \href{http://cran.r-project.org/web/views/WebTechnologies.html}{Web Technologies} (2014-); \href{https://www.github.com/ropensci/opendata}{Open Data} (2015-); \href{https://www.github.com/leeper/PackageDevelopment}{R Package Development} (2015-)}
\entry{Occasional Blogging: \href{http://thomasleeper.com/blog}{Personal academic blog} (2014-); \href{http://ropensci.org/blog/}{rOpenSci} (2014); \href{http://thepoliticalmethodologist.com/2015/01/05/introducing-the-annual-tpm-most-viewed-post-award-and-our-2014-winner/}{\textit{The Political Methodologist}'s Most Viewed Post of 2014}; \href{http://politicalsciencereplication.wordpress.com/}{PoliSci Replication} (2014); \href{https://thewpsa.wordpress.com/2015/05/09/what-can-we-learn-from-10-1-million-facebook-users-its-complicated/}{The New West} (2015-)}

\end{document}
