\documentclass[12pt]{article}
\usepackage{setspace,hyperref,xcolor}
\usepackage[top=1in, bottom=1in, left=1.75in, right=1in, marginparwidth=1.4in]{geometry}
\setlength{\parindent}{-1.55ex}
\usepackage{libertine}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\definecolor{lg}{gray}{0.5} % light-gray definition
\definecolor{mg}{gray}{0.3} % light-gray definition
\definecolor{dg}{gray}{0.0} % dark-gray definition
\color{dg}
\renewcommand{\section}[1]{\pagebreak[3]%
    \llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright {\color{lg}#1}}}}%
    \vspace{-\baselineskip}\par}
\newcommand{\topic}[1]{\pagebreak[3]\indent {\color{lg}{\footnotesize #1 }}\\}
\newcommand{\entry}[1]{\indent {\color{lg}\guillemotright}\hspace{2pt}#1\vspace{.25em}\\}
\newcommand{\subentry}[1]{{\color{lg}-} #1\vspace{.25em}\\}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Curriculum Vitae: Thomas J. Leeper},    % title
    pdfauthor={Thomas J. Leeper},     % author
    pdfsubject={Curriculum Vitae},   % subject of the document
    pdfkeywords={Thomas J. Leeper} {Leeper} {CV} {resume} {research}, % list of keywords
    pdfnewwindow=true,      % links in new window
    pdfborder={0 0 0}
}
\urlstyle{sf}

\begin{document}
{\LARGE Thomas J. Leeper}\\

\today\\

\begin{minipage}[b]{0.5\linewidth}
Department of Government\\
London School of Economics\\
Connaught House 4.11\\
Houghton Street\\
London WC2A 2AE, UK
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
Office Phone (UK): +44 (0)20 7955 7191\\
Voicemail (USA): +1 651 230 7007\\
Email: \href{mailto:thosjleeper@gmail.com}{thosjleeper@gmail.com}\\
Web: \href{http://www.thomasleeper.com/}{http://www.thomasleeper.com/}\\
ORCID: \href{http://orcid.org/0000-0003-4097-6326}{0000-0003-4097-6326}
\end{minipage}\\

\section{Education}
\entry{PhD, Political Science, Northwestern University (2012)}
	\subentry{Dissertation: \textit{Essays on Political Information and the Dynamics of Public Opinion}}
	\subentry{Supervisor: Jamie Druckman}
	\subentry{Committee: Benjamin Page, Dennis Chong, \& Fay Lomax Cook}
\entry{Summer Institute in Political Psychology, Stanford University (2009)}
%\subentry{NU Law School Workshops on Causal Inference (2010) and Bayesian Inference (2011)}
\entry{M.A., Northwestern University (2010)}
%\subentry{Masters Thesis: ``Revisiting Political Awareness: Has Public Opinion Research Forsaken Federalism?'' Committee: Drs. James N. Druckman (Chair) and Dennis Chong.}
\entry{B.A. \textit{magna cum laude} with Distinction, Political Science \& Global Studies, University of Minnesota---Twin Cities (2007)}
%\subentry{Political Science Concentration: Political Psychology, Beliefs, \& Behavior}
%\subentry{Minors: Spanish Studies and Learning Abroad}
%\subentry{Semester Abroad: Fundación Jose Ortega y Gassett, Toledo, Castilla-La Mancha, Spain (2006)}
%\subentry{Honors Thesis, magna cum laude: ``Sympathy, Dissonance, and Affect Transfer: The Electoral Implications of Political Death.'' Adviser: Dr. Joanne Miller.}

\section{Academic Appointments}
\entry{London School of Economics and Political Science}
    \subentry{Associate Professor in Political Behaviour, Government Department (2017--)}
    \subentry{Assistant Professor in Political Behaviour, Government Department (2015--2017)}
    \subentry{Faculty Affiliate, US Centre (2017--)}
    \subentry{Core Group Member, Behavioural Science Hub (2017--)}
\entry{Aarhus University}
    \subentry{Postdoc, Department of Political Science and Government (2013--2015)}
\entry{Northwestern University}
    \subentry{Graduate Fellow, Institute for Policy Research (2009--2012)}

\section{Publications}
\topic{Peer-Reviewed Publications: Political Science}
    \entry{Thomas J. Leeper. 2017. ``Am I a Methodologist? Asking for a Friend.'' \textit{PS: Political Science \& Politics}: In press.}
	\entry{Thomas J. Leeper. 2017. ``How Does Treatment Self-Selection Affect Inferences About Political Communication?'' \textit{Journal of Experimental Political Science}: In press. \href{http://doi.org/10.1017/XPS.2017.1}{doi:10.1017/XPS.2017.1}}
    \entry{Joshua Robison, Thomas J. Leeper, and James N. Druckman. ``Do Heterogeneous Social Networks Undermine Attitude Strength?'' \textit{Political Psychology}. \href{http://doi.org/10.1111/pops.12374}{doi:10.1111/pops.12374}}
	\entry{Kevin J. Mullinix, Thomas J. Leeper, James N. Druckman, and Jeremy Freese. 2015. ``The Generalizability of Survey Experiments.'' \textit{Journal of Experimental Political Science} 2(2): 109--138. \href{http://doi.org/10.1017/XPS.2015.19}{doi:10.1017/XPS.2015.19}}
		\subentry{Media coverage at \href{https://www.washingtonpost.com/news/monkey-cage/wp/2016/03/09/does-social-science-have-a-replication-crisis/}{The Monkey Cage}}
	\entry{Thomas J. Leeper. 2014. ``Cognitive Style and the Survey Response.'' \textit{Public Opinion Quarterly} 78(4): 974--983. \href{http://doi.org/10.1093/poq/nfu042}{doi:10.1093/poq/nfu042}}
	\entry{Thomas J. Leeper. 2014. ``The Informational Basis for Mass Polarization.'' \textit{Public Opinion Quarterly} 78(1): 27--46. \href{http://doi.org/10.1093/poq/nft045}{doi:10.1093/poq/nft045}}
	\entry{Thomas J. Leeper, and Rune Slothuus. 2014. ``Political Parties, Motivated Reasoning, and Public Opinion Formation.'' \textit{Advances in Political Psychology} 35 (Supplement 1): 129--156. \href{http://doi.org/10.1111/pops.12164}{doi:10.1111/pops.12164}}
	\entry{Toby Bolsen, Thomas J. Leeper, and Matthew Shapiro. 2014. ``Doing What Others Do: Norms, Science, and Collective Action on Global Warming.'' \textit{American Politics Research} 42(1): 65--89. \href{http://doi.org/10.1177/1532673X13484173}{doi:10.1177/1532673X13484173}}
	\entry{Toby Bolsen, and Thomas J. Leeper. 2013. ``Self-Interest and Attention to News among Issue Publics.'' \textit{Political Communication} 30(3): 329--348.\\ \href{http://doi.org/10.1080/10584609.2012.737428}{doi:10.1080/10584609.2012.737428}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Learning More from Political Communication Experiments: Pretreatment and Its Effects.'' \textit{American Journal of Political Science} 56(4): 875--896. \href{http://doi.org/10.1111/j.1540-5907.2012.00582.x}{doi:10.1111/j.1540-5907.2012.00582.x}}
	\entry{James N. Druckman, and Thomas J. Leeper. 2012. ``Is Public Opinion Stable? Resolving the Micro-Macro Disconnect in Studies of Public Opinion.'' \textit{Daedalus} 141(4): 50--68. \href{http://doi.org/10.1162/DAED\_a\_00173}{doi:10.1162/DAED\_a\_00173}}
	\entry{James N. Druckman, Jordan Fein, and Thomas J. Leeper. 2012. ``A Source of Bias in Public Opinion Stability.'' \textit{American Political Science Review} 106(2): 430--454.\\ \href{http://doi.org/10.1017/S0003055412000123}{doi:10.1017/S0003055412000123}}

\topic{Peer-Reviewed Publications: Software}
	\entry{Thomas J. Leeper. 2016. ``Crowdsourced Data Preprocessing with R and Amazon Mechanical Turk.'' \textit{R Journal} 8(1): 276--288. \href{https://journal.r-project.org/archive/2016-1/leeper.pdf}{https://journal.r-project.org/archive/2016-1/leeper.pdf}}
	\entry{Thomas J. Leeper. 2014. ``Archiving Reproducible Research with R and Dataverse.'' \textit{R Journal} 6(1): 151--158. \href{http://journal.r-project.org/archive/2014-1/leeper.pdf}{http://journal.r-project.org/archive/2014-1/leeper.pdf}.}

\topic{Chapters in Edited Volumes}
	%\entry{Thomas J. Leeper. ``Measuring Media Effects Outside the Lab.'' In Zoe Oxley and David Redlawsk, eds., \textit{Oxford Encyclopedia of Political Decision Making}.}
    %\entry{Thomas J. Leeper. ``Experimental Methods -- Online/lab.'' In Liz Suhay, Bernard Grofman, and Alex Treschel, eds., \textit{Oxford Handbook of Electoral Persuasion}.}
    \entry{Thomas J. Leeper, and Kevin J. Mullinix. ``Motivated Reasoning.'' In Sandy Maisel, ed., \textit{Oxford Bibliographies in Political Science}. New York: Oxford University Press: In press.}
    \entry{Thomas J. Leeper, and Rune Slothuus. ``Deliberation and Framing.'' In Andre B{\"a}chtiger, John Dryzek, Jane Mansbridge, and Mark Warren, eds., \textit{The Oxford Handbook of Deliberative Democracy}. New York: Oxford University Press. In press.}
	\entry{Samara Klar, and Thomas J. Leeper. N.d. ``Identities and Intersectionality: A Case for Purposive Sampling in Survey Experimental Research.'' In  In Paul J. Lavrakas, Edith de Leeuw, Allyson Holbrook, Courtney Kennedy, Michael W. Traugott, and Brady T. West, eds., \textit{Experimental Methods in Survey Research: Techniques that Combine Random Sampling with Random Assignment}: In press.}
    \entry{James N. Druckman, Thomas J. Leeper, and Kevin J. Mullinix. 2014. ``The Experimental Study of Legislative Behaviors.'' In Thomas Saalfeld, and Kaare Str\o m, eds., \textit{The Oxford Handbook of Legislative Studies}, 194--210. Oxford, UK: Oxford University Press.}
	\entry{Marybeth Neal, Thomas J. Leeper, and Susan Root. 2009. ``Attributes of Quality Service-Learning: Findings from the Transitioning to Adulthood Survey.'' In James C. Kielsmeier, Susan Root, Bjorn Lyngstad, and Caryn Pernu, eds., \textit{Growing to Greatness 2009}. St. Paul: NYLC.}
	\entry{Thomas J. Leeper. 2008. ``Service-Learning in the States: Recent Policy Developments.'' In James C. Kielsmeier, Marybeth Neal, Nathan Schultz, and Thomas J. Leeper, eds. \textit{Growing to Greatness 2008}. St. Paul: NYLC.}
	\entry{Thomas J. Leeper. 2008. ``A Vision of Service-Learning Policy: Why It Matters.'' In James C. Kielsmeier, Marybeth Neal, Nathan Schultz, and Thomas J. Leeper, eds., \textit{Growing to Greatness 2008}. St. Paul: NYLC.}

\topic{Other Academic Publications}
    \entry{Thomas J. Leeper. 2016. ``The Multiple Routes to Credibility.'' \textit{The Political Methodologist} 23(1): 11--16.\\ Available from: \href{https://thepoliticalmethodologist.files.wordpress.com/2016/02/tpm_v23_n1.pdf}{PDF}, \href{https://thepoliticalmethodologist.com/2015/12/21/the-multiple-routes-to-credibility/}{Blog format}.}
	\entry{Thomas J. Leeper. 2014. ``Making High-Resolution Graphics for Academic Publishing.'' \textit{The Political Methodologist} 21(1): 2--5.\\ Available from: \href{https://thepoliticalmethodologist.files.wordpress.com/2014/06/tpm_v21_n12.pdf}{PDF}, \href{https://thepoliticalmethodologist.com/2013/11/25/making-high-resolution-graphics-for-academic-publishing/}{Blog format}}
	\entry{Thomas J. Leeper. 2013. ``Crowdsourcing with R and the MTurk API.'' \textit{The Political Methodologist} 2(2): 2--7.\\ Available from: \href{https://thepoliticalmethodologist.files.wordpress.com/2013/09/tpm_v20_n21.pdf}{PDF}.}
	\entry{Thomas J. Leeper. 2011. ``The Role of Protocol in the Design and Reporting of Experiments.'' \textit{The Experimental Political Scientist} 2(1): 6-10.\\ Available from: \url{http://scholar.harvard.edu/files/dtingley/files/may2011.pdf}}
	\entry{James C. Kielsmeier, Marybeth Neal, Nathan Schultz, and Thomas J. Leeper, eds. 2008. \textit{Growing to Greatness 2008}. St. Paul: National Youth Leadership Council.}
	%\entry{Thomas J. Leeper. 2008. ``Beyond `Valuing Diversity' in Service-Learning.'' \textit{The Generator} 26:3.}
	%\entry{Thomas J. Leeper. 2008. ``Measuring Service-Learning Success.'' \textit{The Generator} 26:2.}
	%\entry{Thomas J. Leeper. 2008. ``Youth Voice Research: Findings, Gaps and Trends.'' \textit{The Generator} 26:1.}

\topic{Book Reviews}
	\entry{Thomas J. Leeper. 2016. ``Book Review: Brian Arbour, \textit{Candidate-Centered Campaigns: Political Messages, Winning Personalities, and Personal Appeals} New York: Palgrave-MacMillan. 2014.'' \textit{Public Opinion Quarterly}: In press. Available from: \href{http://doi.org/10.1093/poq/nfw035}{doi:10.1093/poq/nfw035}}
	\entry{Thomas J. Leeper 2016. ``Book Review: \textit{Political Analysis Using R}.'' \textit{The Political Methodologist} 23(2): 17--19.\\ Available from: \href{https://thepoliticalmethodologist.files.wordpress.com/2016/08/tpm_v23_n2.pdf}{PDF}, \href{https://thepoliticalmethodologist.com/2016/05/25/book-review-political-analysis-using-r/}{Blog format}}

\section{Working Papers\\ \& Ongoing Projects}
\topic{Papers Under Review}
	\entry{Thomas J. Leeper. ``The Roles of Media Choice and Media Effects in Political Knowledge Gaps.'' Revise and Resubmit.}
	\entry{Thomas J. Leeper, and Joshua Robison. ``Proximity Voting in the Age of Elite Polarization.''}
	\entry{Thomas J. Leeper, and Rune Slothuus. ``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.''}
	\entry{Thomas J. Leeper, and Rune Slothuus. ``Using the Rolling Reinterview Design to Study Campaigns, Opinions, and Electoral Behavior.''}
    \entry{C\'{e}line Colombo, Thomas J. Leeper, and Rune Slothuus. ``Enlightening or manipulative? The role of party cues in direct democracy.''}
    \entry{Thomas J. Leeper. ``Causal Effects Under Self-Selection.''}

\topic{Working Papers}
	\entry{Thomas J. Leeper, and Rune Slothuus. ``If Only Citizens Had a Cue: The Process of Opinion Formation over Time''}
	\entry{Thomas J. Leeper. ``Are Important Attitudes More Stable? Revisiting the Evidence.''}
	\entry{Thomas J. Leeper. ``Politics and Media Coverage Shape the Issue Content of the Polling Agenda.''}
	\entry{Thomas J. Leeper, and Emily Thorson. ``Minimial Sponsorship-Induced Bias in Web Survey Data.''}
	\entry{Thomas J. Leeper, and Joshua Robison. ``Political Interest, Audience Size, and Ideology: The Conditional Scope of Selective Exposure to Television.''}
	%\entry{Thomas J. Leeper. ``Information Sources and the Evaluation of Political Arguments.''}
	%\entry{Thomas J. Leeper. ``What Have We Done?! Reporting Political Communication Experiments.''}
	%\entry{Thomas J. Leeper. ``Party and Interest Group Competition over Public Opinions''}
	%\entry{Thomas J. Leeper. ``An Experimental Method for Identifying Inter-Attitudinal Structure''}
    %\entry{Sara B. Hobolt, Thomas J. Leeper, and James Tilley. ``What `Brexit Means Brexit' Means to British Citizens.''}
    %\entry{Sara B. Hobolt, Thomas J. Leeper, and James Tilley. ``Social Perceptions in the British EU Membership Referendum.''}
    %\entry{Sara B. Hobolt, Thomas J. Leeper, and James Tilley. ``Voting among Spousal Dyads.''}
    %\entry{Thomas J. Leeper and Davide Morisi. ``How Do Information and Cues Affect Citizens' Election Forecasts?''}
    % Hix-Kaufmann-Leeper

\section{Grants \&\\Funding}
\topic{External Sources}
	\entry{ESRC Research Grant (ES/R000573/1) (2017), \textsterling120,025, with Sara Hobolt and James Tilley}
    \entry{R Consortium Infrastructure Steering Committee Grant for RL10N Project, \$10,000 (2016)}
	\entry{APSA Annual Meeting Travel Grant, \$300 (2015)}
	\entry{Named project member on Danish Council for Independent Research Sapere Aude grant to Rune Slothuus (DFF--4003-00192B), total award 7,050,249 DKK (approx. \$1,274,748, 2014)}
	\entry{Time-Sharing Experiments for the Social Sciences, approx. \$12,000 (2013)}
	\entry{National Science Foundation Doctoral Dissertation Improvement Grant (SES-1160156), \$12,000 (2012)}
	\entry{APSA Annual Meeting Travel Grant, \$200 (2011)}
	\entry{Bush Foundation Study Abroad Scholarship, University of Minnesota, \$750 (2006)}
	\entry{Hearst Foundation United States Senate Youth Program Scholarship, \$5,000 (2005)}
	
	\topic{Institutional Sources}
	\entry{LSE STICERD Small Grant, \textsterling 4,920 (2017), with Sara Hobolt}
    \entry{LSE Government Department Undergraduate Summer Student Internship Grant (2017)}
    \entry{LSE Research Infrastructure and Investment Fund (1-BRC-A404), \textsterling 11,611 (2016)}
	\entry{LSE Government Departmental Research Fund, \textsterling 4,450 (2016)}
	\entry{LSE Government Department Undergraduate Summer Student Internship Grant (2016)}
	\entry{Northwestern Career Development Grant for Humanists and Social Scientists, \$400 (2012)}
	\entry{Northwestern University TGS Conference Travel Grant, \$500 (2012)}
	\entry{Northwestern University TGS Conference Travel Grant, \$700 (2011)}
	\entry{Weinberg College of Arts and Sciences Humanities and Social Sciences Technology-Enhanced Doctoral Research Award, \$600 (2011)}
	\entry{Northwestern University Graduate Research Grant, \$3,000 (2011)}
	\entry{Northwestern University MacArthur Fund grant, \$2,000 (2009)}
	\entry{Northwestern University Fellowship, \$20,000 (2008-2009, 2012-2013)}

\section{Honors \&\\Awards}
	\entry{Best Paper Award from APSA Elections, Public Opinion, and Voting Behavior Section, with Rune Slothuus (2017)}
	\entry{LSE Promotions Committee Teaching Prize (2017)}
    \entry{Best Paper Award from APSA Experimental Research Section, with Kevin J. Mullinix (2015)}
	\entry{APSA Political Psychology Section Distinguished Junior Scholars Award (2014)}
	\entry{Best Paper Award from APSA Elections, Public Opinion, and Voting Behavior Section (2012)}
	\entry{Timothy Cook Best Graduate Student Paper Award from APSA Political Communication Section (2012)}
	\entry{Honorable Mention, National Science Foundation Graduate Research Fellowship (2009)}
	\entry{Early election, Phi Beta Kappa, University of Minnesota (2007)}
	\entry{College of Liberal Arts Undergraduate Honors Program, University of Minnesota (2006-2007)}
	\entry{College of Liberal Arts Dean's List, University of Minnesota (2005-2007)}
	\entry{Minnesota Delegate, United States Senate Youth Program (2005)}

\section{Invited\\Presentations\\\& Conference\\Papers}
	%\topic{Invited Presentations (2018)}
    %\entry{``The Generalizability of Heterogeneous Treatment Effects.'' Center for Statistics and the Social Sciences, University of Washington, Seattle, Washington, US.}

    \topic{Invited Presentations (2017)}
	\entry{``What `Brexit Means Brexit' Means to British Citizens.'' Department of Politics and Public Administration Colloquium, University of Konstanz.}
    \entry{``Social Perceptions in the British EU Membership Referendum.'' University of Vienna, Vienna, Austria.}
    \entry{``How Do Information and Cues Affect Citizens' Election Forecasts?'' Government Department Colloquium, London School of Economics and Political Science.}
    \entry{``Social Perceptions in the British EU Membership Referendum.'' University of Zurich/ETH Zurich Comparative and International Studies Colloquium, Zurich, Switzerland.}
	
	\topic{Invited Presentations (2016)}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' University of Essex, Colchester, UK.}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' The Ohio State University, Columbus, Ohio.}
	\entry{``The Information Environment and Consistency in Citizens' Policy Opinions.'' National Research University Higher School of Economics, Moscow, Russia.}
	\entry{``Social Identity Cues and the EU Referendum.'' Nuffield College, Oxford University, Oxford, United Kingdom.}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' Universitat Pompeu Fabra, Barcelona, Spain.}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' Democracy, Elections, and Citizenship Group, Universistat Autonoma de Barcelona, Barcelona, Spain.}
	\entry{``The Information Environment and Consistency in Citizens' Policy Opinions.'' Mapping Political Preferences Conference, Institute for Advanced Study-Toulouse, Toulouse, France.}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' Political Behaviour Workshop, Department of Government, London School of Economics and Political Science.}

	\topic{Invited Presentations (2015)}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' European University Institute, Firenze, Italy.}
	\entry{``What If You Had Done Things Differently? Testing the Generalizability of Framing Effects with Parallel Experiment.'' Workshop on Innovations in Online Experiments, Nuffield College, Oxford, UK.}
	
	\topic{Invited Presentations (2014)}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' Manship School of Mass Communication, Louisiana State University.}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' Department of Political Science, McGill University.}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' Department of Government, London School of Economics and Political Science.}
	\entry{``Why Do We Execute?'' Political Behavior Workshop, Aarhus University.}
	\entry{``Reproducible Research: What, Why, How.'' Interacting Minds Centre, Aarhus University.}
	\entry{``How Real-World Political Debate Influences Public Opinion Formation and Experimental Effects on Opinion.'' Experiments in Political Science Workshop, Copenhagen University.}

	\topic{Invited Presentations (2013)}
	\entry{``To Whom, With What Effect? Parallel Experiments on Framing.'' Comparative Politics Workshop, Aarhus University.}
	\entry{``Beyond Approach/Avoidance in Political Psychology.'' Political Behavior Workshop, Aarhus University.}
	\entry{``To Whom, With What Effect? Parallel Experiments on Framing.'' Department of Political Science and Public Management, University of Southern Denmark.}
	\entry{``Interest Groups and Political Attitudes.'' Comparative Politics Workshop, Aarhus University.}
	
	\topic{Invited Presentations (2012 and earlier)}
	\entry{``Political Groups and Public Opinion.'' Political Parties Working Group, Northwestern University, 2012.}
	\entry{``Strong Attitudes and Biased Political Engagement.'' American Politics Workshop, Northwestern University, 2012.}
	\entry{``The Problem with Captive Audiences: Framing and Information Search.'' Applied Quantitative Methods Workshop, Northwestern University, 2011.}
	\entry{``Bias in Political Communication Experiments.'' Political Psychology Workshop, University of Chicago, 2011.}
	\entry{``Revisiting Political Awareness: Has Public Opinion Research Forsaken Federalism?'' American Politics Workshop, Northwestern University, 2010.}

	\topic{Conference Papers (2017)}
    \entry{``What `Brexit Means Brexit' Means to British Citizens.'' Elections, Public Opinion, and Parties Annual Conference, Nottingham, UK.}
	\entry{``The Replicability of Heterogeneous Treatment Effects Estimates Across Samples.'' Annual meeting of the American Political Science Association, San Francisco, California.}
    \entry{``Can Citizens Be Framed? How Information More than Emphasis Changes Opinions.'' Annual meeting of the American Political Science Association, San Francisco, California.}
    \entry{``Social Perceptions in the British EU Membership Referendum.'' Annual scientific meeting of the International Society for Political Psychology, Edinburgh, Scotland.}
    \entry{``Tools for Quantitative Methods.'' The Gold Standard of Reproducible Research Workshop, University of Nottingham.}
	
    \topic{Conference Papers (2016)}
	\entry{``If Only Citizens Had a Cue: The Process of Opinion Formation over Time.'' Annual meeting of the American Political Science Association, Philadelphia, PA.}
	\entry{``Proximity Voting in the Age of Elite Polarization.'' Annual meeting of the American Political Science Association, Philadelphia, PA.}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' Annual scientific meeting of the International Society for Political Psychology, Warsaw, Poland.}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' Annual meeting of the European Political Science Association, Brussels, Belgium.}
	
	\topic{Conference Papers (2015)}
	\entry{``Can Citizens Be Framed? How Information, Not Emphasis, Changes Opinions.'' Amsterdam Political Psychology Conference, Amsterdam, Netherlands.}
	\entry{``The Nonrandom Polling of Public Opinion.'' Annual meeting of the American Political Science Association, San Francisco, CA.}
	\entry{``Political Interest, Audience Size, and Ideology: The Conditional Scope of Selective Exposure to Television.'' APSA Pre-Conference on Political Communication, San Francisco, CA.}
	\entry{``Crowdsourced Data Processing with MTurkR.'' The useR! Conference, Aalborg, Denmark.}
	\entry{``The Information Environment and Consistency in Citizens' Policy Opinions.'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	\entry{``The Role of Media Choice and Media Effects in Political Knowledge Gaps.'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	\entry{``Sponsorship-Induced Bias in Online Survey and Experimental Data.'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	
	\topic{Conference Papers (2014)}
	\entry{``Unifying Theory and Methods on the Effects of Political Information Exposure.'' Danish Political Science Association Annual Meeting, Vejle, Denmark.}
	\entry{``To Whom, and With What Effect? Parallel Experiments on Framing.'' Annual meeting of the American Political Science Association, Washington, DC.}
	\entry{``How Real-World Political Debate Influences Public Opinion Formation and Experimental Effects on Opinion.'' Annual meeting of the American Political Science Association, Washington, DC.}
	\entry{``How Real-World Political Debate Influences Public Opinion Formation and Experimental Effects on Opinion.'' Nordic Political Science Association Conference, Gothenburg, Sweden. (Declined)}
	\entry{``Are Strong Opinions More Stable?'' Annual scientific meeting of the International Society for Political Psychology, Rome, Italy.}
	\entry{``To Whom, and With What Effect? Parallel Experiments on Framing.'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	\entry{``Are Strong Opinions More Stable?'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	
	\topic{Conference Papers (2013)}
	\entry{``Interest Groups and Political Attitudes.'' Danish Political Science Association Annual Meeting, Vejle, Denmark.}
	\entry{``Byproduct Exposure to Politics'' Annual meeting of the American Political Science Association, Chicago, IL.}
	\entry{``In Search of Political Attitude Structure.'' Annual scientific meeting of the International Society for Political Psychology, Herzliya, Israel. (Declined)}
	\entry{``Preference-based Measures of Media Exposure.'' Annual conference of the American Association for Public Opinion Research, Boston, MA.}
	
	\topic{Conference Papers (2012)}
	\entry{``Strong Attitudes and Biased Political Engagement.'' Annual meeting of the American Political Science Association, New Orleans, LA.}
	\entry{``The Informational Basis of Mass Polarization.'' Annual scientific meeting of the International Society for Political Psychology, Chicago, IL.}
	\entry{``Strong Attitudes and Biased Political Engagement.'' Annual scientific meeting of the International Society for Political Psychology, Chicago, IL.}
	\entry{``Strong Attitudes and Biased Political Engagement.'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	\entry{``Getting Informed or Just Getting By: How Attentive Do Citizens Need to Be to `Get' the News?'' Annual meeting of the Midwest Political Science Association, Chicago, IL.}
	
	\topic{Conference Papers (2011 and earlier)}
	\entry{``Learning More from Political Communication Experiments: The Importance of Pretreatment Effects.'' Annual meeting of the American Political Science Association, Seattle, IL, 2011.}
	\entry{``The Problem with Captive Audiences: Framing and Information Search.'' Annual meeting of the American Political Science Association, Seattle, IL, 2011.}
	\entry{``Matching Moderators: Causal Interactions in Observational Studies.'' Annual meeting of the Midwest Political Science Association, Chicago, IL, 2011.}
	\entry{``Bias in Political Communication Experiments.'' Annual meeting of the Midwest Political Science Association, Chicago, IL, 2011.}
	\entry{``Revisiting Political Awareness: Has Public Opinion Research Forsaken Federalism?'' Annual meeting of the Midwest Political Science Association, Chicago, IL, 2010.}
	%\entry{``Attributes of Quality Service-Learning in Respondent's Past Service Experience: New Findings from NYLC's Transitioning To Adulthood Survey.'' Presented at the International Research Conference on Service-Learning and Civic Engagement, New Orleans, 2008.}

\section{Software}
\topic{R Packages}
	\entry{``arco: Pick a Color From a Tcl/tk chooseColor Widget.'' On \href{https://github.com/leeper/arco}{GitHub}.}
	\entry{``bib2df: Parse a .bib-file to a data frame.'' On \href{https://cran.r-project.org/package=bib2df}{CRAN}, \href{https://github.com/ottlngr/bib2df}{GitHub}.}
	\entry{``colourlovers: R client for the COLOURlovers API.'' On \href{https://cran.r-project.org/package=colourlovers}{CRAN}, \href{https://github.com/leeper/colourlovers}{GitHub}.}
	\entry{``crandatapkgs: Find Data-Only Packages on CRAN.'' On \href{https://cran.r-project.org/package=crandatapkgs}{CRAN}, \href{https://github.com/leeper/crandatapkgs}{GitHub}.}
	\entry{``csvy: Import and Export CSV Data With a YAML Metadata Header.'' On \href{https://cran.r-project.org/package=csvy}{CRAN}, \href{https://github.com/leeper/csvy}{GitHub}.}
	\entry{``dtupdate: Functions that try to make it easier to keep up with the non-CRAN universe.'' On \href{https://github.com/hrbrmstr/dtupdate}{GitHub} (Contributor).}
	\entry{``ggparliament: Parliament Plots.'' On \href{https://github.com/leeper/ggparliament}{GitHub}.}
    \entry{``GK2011: Gaines and Kuklinski (2011) Estimators for Hybrid Experiments.'' On \href{https://cran.r-project.org/package=GK2011}{CRAN}, \href{https://github.com/leeper/GK2011}{GitHub}.}
	\entry{``lumendb: Lumen Database API Client.'' On \href{https://cran.r-project.org/package=lumendb}{CRAN}, \href{https://github.com/leeper/lumendb}{GitHub}.}
	\entry{``margins: Marginal Effects for Model Objects.'' On \href{https://cran.r-project.org/package=margins}{CRAN}, \href{https://github.com/leeper/margins}{GitHub}.}
	\entry{``mcode: Functions to merge and recode across multiple variables.'' On \href{https://github.com/leeper/mcode}{GitHub}.}
	\entry{``meme: Meme Generation in R.'' On \href{https://github.com/leeper/meme}{GitHub}.}
	\entry{``prediction: Tidy, Type-safe `prediction()' Methods.'' On \href{https://cran.r-project.org/package=prediction}{CRAN}, \href{https://github.com/leeper/prediction}{GitHub}.}
	\entry{``responserates: AAPOR Survey Response Rates.'' On \href{https://github.com/leeper/responserates}{GitHub}.}
	\entry{``rio: A Swiss-army Knife for Data File I/O.'' On \href{https://cran.r-project.org/package=rio}{CRAN}, \href{https://github.com/leeper/rio}{GitHub}.}
	\entry{``rio.db: A Database Extension for `rio'.'' On \href{https://github.com/leeper/rio.db}{GitHub}.}
	\entry{``rite: The Right Editor to Write R.'' On \href{https://cran.r-project.org/package=rite}{CRAN}, \href{https://github.com/leeper/rio}{GitHub}.}
	\entry{``rpublons: Client for Publons.com.'' On \href{https://github.com/leeper/publons}{GitHub}.}
	\entry{``slopegraph: Edward Tufte-inspired Slopegraphs in R.'' On \href{https://github.com/leeper/slopegraph}{GitHub}.}
	\entry{``sparktex: Generate LaTeX sparklines in R.'' On \href{https://cran.r-project.org/package=sparktex}{CRAN}, \href{https://github.com/leeper/sparktex}{GitHub}.}
	\entry{``ukbabynames: UK Baby Names Data.'' On \href{https://cran.r-project.org/package=ukbabynames}{CRAN}, \href{https://github.com/leeper/ukbabynames}{GitHub}.}
	\entry{``UNF: Tools for Creating Universal Numeric Fingerprints for Data.'' On \href{https://cran.r-project.org/package=UNF}{CRAN}, \href{https://github.com/leeper/UNF}{GitHub}.}
	\entry{``webuse: Import Stata 'webuse' Datasets.'' On \href{https://cran.r-project.org/package=webuse}{CRAN}, \href{https://github.com/leeper/webuse}{GitHub}.}
	\entry{Other assorted code samples are available on \href{http://github.com/leeper}{GitHub}.}

	\topic{R packages contributed to the cloudyr project}
	\entry{``appveyor: Appveyor API Client Package.'' On \href{https://github.com/cloudyr/appveyor}{GitHub}.}
	\entry{``awspack: Amazon Web Services Bundle Package.'' On \href{https://cran.r-project.org/package=awspack}{CRAN}, \href{https://github.com/cloudyr/awspack}{GitHub}.}
	\entry{``aws.cloudwatch: Amazon Web Services Cloudwatch Client.'' On \href{https://github.com/cloudyr/aws.cloudwatch}{GitHub}.}
	\entry{``aws.cloudtrail: Amazon Web Services Cloudtrail Client.'' On \href{https://cran.r-project.org/package=aws.cloudtrail}{CRAN}, \href{https://github.com/cloudyr/aws.cloudtrail}{GitHub}.}
	\entry{``aws.code: Amazon Web Services CodeCommit Client.'' On \href{https://github.com/cloudyr/aws.code}{GitHub}.}
	\entry{``aws.ec2: Amazon Web Services EC2 Client.'' On \href{https://github.com/cloudyr/aws.ec2}{GitHub}.}
	\entry{``aws.ec2metadata: Get EC2 Instance Metadata.'' On \href{https://cran.r-project.org/package=aws.ec2metadata}{CRAN}, \href{https://github.com/cloudyr/aws.ec2metadata}{GitHub}.}
	\entry{``aws.efs: Amazon Web Services EFS Client.'' On \href{https://github.com/cloudyr/aws.efs}{GitHub}.}
	\entry{``aws.glacier: Amazon Web Services Glacier Client.'' On \href{https://github.com/cloudyr/aws.glacier}{GitHub}.}
	\entry{``aws.iam: Amazon Web Services IAM Client.'' On \href{https://cran.r-project.org/package=aws.iam}{CRAN}, \href{https://github.com/cloudyr/aws.iam}{GitHub}.}
	\entry{``aws.lambda: Amazon Web Services Lambda Client.'' On \href{https://cran.r-project.org/package=aws.lambda}{CRAN}, \href{https://github.com/cloudyr/aws.lambda}{GitHub}.}
	\entry{``aws.polly: Client for Amazon Polly.'' On \href{https://cran.r-project.org/package=polly}{CRAN}, \href{https://github.com/cloudyr/aws.polly}{GitHub}.}
	\entry{``aws.s3: Amazon Web Services Simple Storage Service Client.'' On \href{https://cran.r-project.org/package=aws.s3}{CRAN}, \href{https://github.com/cloudyr/aws.s3}{GitHub}.}
	\entry{``aws.ses: Amazon Web Services Simple Email Service Client.'' On \href{https://cran.r-project.org/package=aws.ses}{CRAN}, \href{https://github.com/cloudyr/aws.ses}{GitHub}.}
	\entry{``aws.signature: Amazon Web Services Request Signatures.'' On \href{https://cran.r-project.org/package=aws.signature}{CRAN}, \href{https://github.com/cloudyr/aws.signature}{GitHub}.}
	\entry{``aws.sns: Amazon Web Services Simple Notification Service Client.'' On \href{https://cran.r-project.org/package=aws.sns}{CRAN}, \href{https://github.com/cloudyr/aws.sns}{GitHub}.}
	\entry{``aws.sqs: Amazon Web Services Simple Queue Service Client.'' On \href{https://cran.r-project.org/package=aws.sqs}{CRAN}, \href{https://github.com/cloudyr/aws.sqs}{GitHub}.}
	\entry{``cirleci: Circle CI API Client Package.'' On \href{https://github.com/cloudyr/circleci}{GitHub}.}
	\entry{``crowdflower: Crowdflower.com R Client.'' On \href{https://github.com/cloudyr/crowdflower}{GitHub} (with Ken Benoit and Pablo Barber\'{a}).}
	\entry{``ghit: Lightweight GitHub Package Installer.'' On \href{https://cran.r-project.org/package=ghit}{CRAN}, \href{https://github.com/cloudyr/ghit}{GitHub}.}
	\entry{``imguR: Imgur API Client Package for R.'' On \href{https://cran.r-project.org/package=imguR}{CRAN}, \href{https://github.com/cloudyr/imguR}{GitHub}.}
	\entry{``microworkers: Microworkers.com R Client.'' On \href{https://github.com/cloudyr/microworkers}{GitHub}.}
	\entry{``MTurkR: R Client for the MTurk Requester API.'' On \href{https://cran.r-project.org/package=MTurkR}{CRAN}, \href{https://github.com/leeper/MTurkR}{GitHub}.}
	\entry{``MTurkRGUI: A Graphical User Interface for MTurkR.'' On \href{https://cran.r-project.org/package=MTurkRGUI}{CRAN}, \href{https://github.com/leeper/MTurkRGUI}{GitHub}.}
	%\entry{``Rmonkey: Access Survey Monkey from R.'' On \href{https://cran.r-project.org/package=Rmonkey}{CRAN}, \href{https://github.com/cloudyr/Rmonkey}{GitHub}.}
	\entry{``rscribd: Scribd API Client Package for R.'' On \href{https://github.com/cloudyr/rscribd}{GitHub}.}
	\entry{``travisci: Travis-CI API Client Package.'' On \href{https://github.com/cloudyr/travisci}{GitHub}.}

	\topic{R packages contributed to RL10N}
	\entry{``msgtools: Tools for Developing Diagnostic Messages.'' On \href{https://github.com/RL10N/msgtools}{GitHub}.}

	\topic{R packages contributed to the rOpenSci project}
	\entry{``dvn: Access to The Dataverse Network APIs.'' On \href{https://cran.r-project.org/package=dvn}{CRAN}.}
	\entry{``dataverse: R Dataverse Client.'' On \href{https://cran.r-project.org/package=dataverse}{CRAN}, \href{https://github.com/iqss/dataverse-client-r}{GitHub} (in collaboration with Harvard--IQSS).}
	\entry{``tabulizer: Bindings for Tabula PDF Table Extractor Library.'' On \href{https://github.com/ropensci/tabulizer}{GitHub}.}

	\topic{R packages contributed to the rOpenGov project}
	\entry{``dkstat: API connection to the StatBank from Statistics Denmark..'' On \href{https://github.com/rOpenGov/dkstat}{GitHub} (Contributor).}
	\entry{``federalregister: R client for the U.S. Federal Register API.'' On \href{https://cran.r-project.org/package=federalregister}{CRAN}, \href{https://github.com/rOpenGov/federalregister}{GitHub}.}
	\entry{``mpg: Fuel economy data from FuelEconomy.gov.'' On \href{https://github.com/rOpenGov/mpg}{GitHub}.}
	\entry{``pollstR: R client for the Pollster API.'' On \href{https://cran.r-project.org/package=pollstR}{CRAN} (Contributor).}
	\entry{``RPublica: ProPublica API Client.'' On \href{https://cran.r-project.org/package=RPublica}{CRAN}, \href{https://github.com/rOpenGov/RPublica}{GitHub}.}
	\entry{``rsunlight. Interface to APIs for data on what our elected representatives are up to.'' On \href{https://cran.r-project.org/package=rsunlight}{CRAN} (Contributor).}
	\entry{``usbroadband: Data for the U.S. National Broadband Map.'' On \href{https://github.com/rOpenGov/usbroadband}{GitHub}.}

    \topic{R packages contributed to the rOpenHealth project}
	\entry{``openfda: Convenient access to the OpenFDA API.'' On \href{https://github.com/ropenhealth/openfda}{GitHub} (Contributor).}

	\topic{Stata Packages}
	\entry{``ciplotm: Modified Version of Nick Cox's `ciplot'.'' On \href{https://github.com/leeper/ciplotm}{GitHub}.}

%\clearpage
\section{Teaching \&\\ Advising}
\topic{Lecturing: London School of Economics and Political Science}
	\entry{\textit{Experimental Politics} (Bachelor), LSE, 2017/18--}
	\entry{\textit{Research Design in Political Science} (PhD), LSE, 2017/18--}
	\entry{\textit{Public Opinion, Political Psychology, and Citizenship} (Master), LSE, 2016--}
	\entry{\textit{Research Design in Political Science} (Bachelor), LSE, 2015/16--}

\topic{Lecturing: Aarhus University}
	\entry{\textit{Surveys for Research and Evaluation} (Master), Aarhus University, 2014}
	\entry{\textit{Issues in American Politics and Government} (Master), Aarhus University, 2014}
	\entry{\textit{Experimentation and Causal Inference} (Master), Aarhus University, 2014}
	\entry{\textit{Quantitative Political Analysis} (Master/PhD), Aarhus University, 2014--15}
	\entry{\textit{Does Public Opinion Matter?} (Master), Aarhus University, 2013}

\topic{Class Teaching: Northwestern University}
	\entry{TA, \textit{Statistical Research Methods} (Bachelor), Northwestern University, 2011} % Jason Seawright
	\entry{TA, \textit{Methods of Political Inference} (Bachelor), Northwestern University, 2011} % Jim Mahoney
	\entry{TA, \textit{Political Psychology of Mass Behavior} (Bachelor), University of Minnesota, 2007} % Chris Galdieri

\topic{Short courses}
	\entry{``Version Control and Dynamic Documents.'' BITSS RT2 Workshop, London, UK, 2017.}
    \entry{``Experimental Research in Legislative Studies.'' ECPR Summer School on Parliaments, Humboldt University Berlin, Germany, 2017.}
    \entry{``Survey Experiments.'' NTNU, Norwegian University of Science and Technology, Trondheim, Norway, 2017.}
	\entry{``Survey Experiments.'' European University Institute, Firenze, Italy, 2017.}
	\entry{``Survey Experiments.'' Barcelona Summer School in Survey Methodology, Universitat Pompeu Fabra, 2016,17.}
	\entry{``Online Surveys and Online Experiments.'' European University Institute, Firenze, Italy, 2015.}
	\entry{``Regression Computation.'' PhD Course, Department of Political Science and Government, Aarhus University, 2015.}
	\entry{``Producing Reproducible Research.'' Interacting Minds Center, Aarhus University, 2014.}
	\entry{``Introduction to R.'' Department of Political Science and Government, Aarhus University, 2013.}

\topic{PhD Supervision}
    \entry{Elena Pupaza (co-supervisor with Michael Bruter)}
    %\entry{}

\topic{Master Thesis Supervision}
	\entry{London School of Economics and Political Science}
		%\subentry{2018: }
        \subentry{2017: Svetlana Bilalova, Ohad Gutman, Charles Lasswell, Ann Bandolik, Robert Baron}
	\entry{Aarhus University}
		\subentry{2015: Jakob Stensg{\aa}rd}

\topic{External Examining}
    \entry{LSE European Institute: Diane Bolet (PhD Upgrade, 2017)}
    \entry{University of Greenwich: Nigel Gervas (MRes, 2017)}

\topic{Pedagogical Qualifications}
    \entry{Postgraduate Certificate in Higher Education (Full Level), London School of Economics and Political Science (In progress)}
    \entry{Postgraduate Certificate in Higher Education (Associate Level), London School of Economics and Political Science (2016)}
	
\topic{Pedagogical Training}
	\entry{Participant, Teaching and Learning Centre Research Methods Teaching Practice and Exchange Forum, 2015--}
	\entry{Various Academic Development Programme workshops, London School of Economics and Political Science, 2015--Present}
	\entry{Educational IT -- Go Online Course, Aarhus University, 2013}
	\entry{Teaching Training Programme for Assistant Professors and Postdocs, Aarhus University, 2013}
	\entry{New Teaching Assistant Conference, Northwestern University, 2010}

\section{Editing \&\\ Reviewing}
\topic{Editing}
	\entry{Editorial Board, \href{http://www.tandfonline.com/toc/upcp20/current}{\textit{Political Communication}} (2017--2020)}
    \entry{Editorial Board, \href{http://joss.theoj.org/}{\textit{Journal of Open Source Software}} (2017--)}
    \entry{Editorial Board, \href{http://link.springer.com/journal/11109}{\textit{Political Behavior}} (2016--2019)}
	\entry{Editorial Board, \href{http://riojournal.com/}{\textit{Research Ideas and Outcomes}} (2015--)}
	\entry{Associate PI, Time-Sharing Experiments for the Social Sciences (2013--)}

\topic{Peer Review Activity}
	\entry{Journal Reviewer (see \href{https://publons.com/a/634082/}{Publons Profile}):\\\textit{American Journal of Political Science}, \textit{American Political Science Review}, \textit{American Politics Research}, \textit{British Journal of Political Science}, \textit{Comparative Political Studies}, \textit{DATABASE: The Journal of Biological Databases and Curation}, \textit{European Union Politics}, \textit{Field Methods}, \textit{Future Internet}, \textit{International Journal of Public Opinion Research}, \textit{Irish Political Studies}, \textit{Japanese Journal of Political Science}, \textit{Journal of Communication}, \textit{Journal of Elections, Public Opinion, and Parties}, \textit{Journal of Ethnic and Migration Studies}, \textit{Journal of Experimental Political Science}, \textit{Journal of Politics}, \textit{Journal of Public Policy}, \textit{Journal of Women, Politics \& Policy}, \textit{Journalism \& Mass Communication Quarterly}, \textit{Nature Climate Change}, \textit{PLoS One}, \textit{Political Analysis}, \textit{Political Behavior}, \textit{Political Communication}, \textit{Political Psychology}, \textit{Political Research Quarterly}, \textit{Political Science Research and Methods}, \textit{Politics, Groups, and Identities}, \textit{PS: Political Science \& Politics}, \textit{Public Administration}, \textit{Public Opinion Quarterly}, \textit{Quarterly Journal of Political Science}, \textit{Research \& Politics}, \textit{R Journal}, \textit{SAGE Open}, \textit{Scandinavian Political Studies}, \textit{Science}, \textit{Social Science Computer Review}}
	\entry{Funding Reviewer: Israeli Science Foundation, Netherlands Organisation for Scientific Research, U.K. Economic and Social Research Council, U.S. National Science Foundation}
	\entry{Book Reviewer: Cambridge University Press, MIT Press, Routledge Press, SAGE Publications}
	\entry{Other Peer Review Activity:\\ AAPOR Annual Conference, Center for Experimental Social Science at Nuffield College--Oxford, rOpenSci R Package Onboarding, TESS: Time-Sharing Experiments for the Social Sciences}

\section{Institutional\\ \& Professional Service}
\topic{Institutional (London School of Economics and Political Science)}
	\entry{Member, Research Ethics Committee (2016--2019)}
	
\topic{Departmental (London School of Economics and Political Science)}
	\entry{BSc Programme Director (2017--2020)}
    \entry{Member, Teaching Committee (2017--)}
    \entry{Organizer, Political Behaviour Seminar (2016--)}
	\entry{Member, Doctoral Programme Committee (2016--)}
    \entry{Search committee, EUDEMOS project Postdoc (2016)}
	\entry{Faculty Participant, Government Department Townhall (2015--)}
	\entry{Discussant, Undergraduate Political Review Colloquium (2016)}
    \entry{Recruitment and Outreach Events}
        \entry{Presenter, LSE Open Day (2016, 2017)}

\topic{Departmental (Northwestern University)}
	\entry{Co-Chair, Northwestern Political Science Commune (Graduate student organization) (2011-2012)}
	\entry{Coordinator, Undergraduate Political Science Experimental Research Participation Pool (2010-2012)}

\topic{Disciplinary Committees}
		\subentry{At-Large Member, APSA Political Communication Executive Committee (2016--2017)}
		\subentry{Member, rOpenSci Unconf Nominations Committee (2016)}
		\subentry{Member, APSA EPOVB Section Graduate Student Travel Award Committee (2016)}
		\subentry{Member, APSA Political Communication Section Nominating Committee (2016)}
		\subentry{Member, APSA Political Psychology Career Achievement Award Committee (2015)}
		\subentry{Member, APSA Political Communication Section Doris Graber Book Award Committee (2014)}
		\subentry{Member, APSA Political Psychology Section Best Paper Award Committee (2014)}

\topic{Service at Professional Conferences}
    \entry{Conference Programme Chair}
        \subentry{APSA Public Opinion Division (2018)}
        \subentry{MPSA Experimental Research Division (2014)}
	\entry{Other}
        \subentry{Panel Discussant:\\ AAPOR (2013), APSA (2012, 2014, 2015, 2016, 2017), DPSA (2013, 2014), MPSA (2014, 2015), EPSA (2016)}
		\subentry{Panel Chair:\\ APSA (2013, 2017), ISPP (2012, 2013, 2014, 2017), MPSA (2014, 2015)}
		\subentry{Roundtable participant:\\ MPSA (2015), ISPP (2016)}
		\subentry{Panel Organizer: ``Advances in Experiments on Media and Information Choices'' (APSA 2013)}

\topic{Professional Memberships:}
		\subentry{American Political Science Association}
		\subentry{European Political Science Association}
        \subentry{Society for Political Methodology}
		\subentry{American Association for Public Opinion Research}
		\subentry{International Society for Political Psychology}
		\subentry{Associate Fellow, Higher Education Academy (2016--)}
        \subentry{Midwest Political Science Association (2009--2014)}
		
\section{Public\\ Engagement}
	\topic{Open Science Evangelism}
		\subentry{Catalyst, \href{http://www.bitss.org/}{Berkeley Institute for Transparency in the Social Sciences} (2017-)}
		\subentry{Co-Founder, \href{http://rl10n.github.io/}{RL10N: An R Localization Project} (2016-) with Richard Cotton}
		\subentry{Founder, \href{http://cloudyr.github.io/}{the cloudyr project} (2014-)}
		\subentry{Contributing developer, \href{http://ropensci.org/}{rOpenHealth} (2015-)}
		\subentry{Contributing developer, \href{http://ropensci.org/}{rOpenSci} (2014-)}
		\subentry{Contributing developer, \href{http://ropengov.github.io/}{rOpenGov} (2014-)}
		\subentry{Co-maintainer, \href{http://cran.r-project.org/web/views/WebTechnologies.html}{CRAN Web Technologies Task View} (2014-)}
		\subentry{Co-maintainer, \href{https://www.github.com/ropensci/opendata}{R Open Data Task View} (2015-)}
		\subentry{Co-maintainer, \href{https://www.github.com/leeper/PackageDevelopment}{R Package Development Task View} (2015-)}
		\subentry{Participant, rOpenSci Unconf (2016)}
	
	\topic{Media Coverage and Interviews}
        \subentry{\href{http://www.newstatesman.com/politics/uk/2017/07/why-labour-lost-and-how-it-can-win-essay-rebuilding-broad-church}{``Why Labour lost and how it can win: an essay on rebuilding a broad church.''} \textit{The New Statesman} (2017)}
		\subentry{\href{https://cincodias.elpais.com/cincodias/2017/06/07/mercados/1496862592_391146.html}{``Londres y la libra reavivan el fantasma del `brexit' ''} \textit{El Pais CincoD\'{i}as} (2017)}
        \subentry{\href{http://www.ceskenoviny.cz/zpravy/mayova-nezvladla-kampan-malo-rekla-o-brexitu-mini-experti/1494511}{``Mayov\'{a} nezvl\'{a}dla kampa\v{n}, m\'{a}lo \v{r}ekla o brexitu, m\'{i}n\'{i} experti''} \textit{\v{C}esk\'{e} Noviny} (2017)}
        \subentry{\href{http://www.tyden.cz/rubriky/zahranici/evropa/na-volby-nebudou-mit-utoky-zadny-vliv-mini-londynane_433320.html}{``Na volby nebudou m\'{i}t \'{u}toky \v{z}\'{a}dn\'{y} vliv, m\'{i}n\'{i} Lond\'{y}\v{n}an\'{e}''} \textit{T\'{y}den} (2017)}
		\subentry{RAI News24 (2017)}
        \subentry{\href{https://inews.co.uk/essentials/news/world/donald-trumps-revelations-russia-may-legal-thats-not-point/}{``Donald Trump's revelation to Russia may be legal, but that's not the point''} \textit{iNews} (2017)}
        \subentry{\href{http://www.bbc.com/mundo/noticias-internacional-37701880}{Why in US democracy is the vote indirect and how does the Electoral College actually work?} \textit{BBC Mundo} (2016)}
		\subentry{\href{https://inews.co.uk/essentials/news/world/us-elections-nasty/}{``Why Are US Elections So Nasty?''} \textit{iNews} (2016)}
		\subentry{\href{https://inews.co.uk/essentials/news/world/moustafa-bayoumi-retweeted-50000-presidential-debate/}{``Why Moustafa Bayoumi was retweeted 50,000 times during the presidential debate''} \textit{iNews} (2016)}
		\subentry{\href{https://www.youtube.com/watch?v=Hwm5V6H_qog&list=PLK4elntcUEy1a8P47lFQDg1oHoNq1BdYk&index=20}{LSE Communications Interview for \#LSEUSElects YouTube Series (2016)}}
		\subentry{\href{https://inews.co.uk/explainers/iq/candidates-stand-us-election-2016/}{``US election 2016: Where do the candidates stand?''} \textit{iNews} (2016)}
		\subentry{\href{http://videnskab.dk/kultur-samfund/facebook-forskning-overrasker-demokratiet-er-mindre-udfordret-end-vi-troede}{``Facebook-forskning overrasker: Demokratiet er mindre udfordret, end vi troede''} \textit{Videnskab.dk} (2015)}
	
	\topic{Occasional Blogging}
		\entry{\href{http://thomasleeper.com/blog}{Academic blog} (2014-)}
		\entry{UK in a Changing Europe}
			\subentry{\href{http://ukandeu.ac.uk/pitfalls-in-releasing-research-findings-on-brexit/}{``Pitfalls in releasing research findings on Brexit''} (2017)}
		\entry{LSE Brexit Blog}
			\subentry{\href{http://blogs.lse.ac.uk/brexit/2017/09/22/disappointment-all-round-experts-respond-to-the-florence-speech/}{``Disappointment all round: experts respond to the Florence speech.''} (2017)}
            \subentry{\href{http://blogs.lse.ac.uk/brexit/2017/08/13/the-british-are-indifferent-about-many-aspects-of-brexit-but-leave-and-remain-voters-are-divided-on-several-key-issues/}{``The British are indifferent about many aspects of Brexit, but Leave and Remain voters are divided on several key issues''} (2017)}
		\entry{LSE Government Department Blog}
			\subentry{\href{http://blogs.lse.ac.uk/government/2017/01/09/the-world-is-right-to-be-concerned-by-donald-trumps-unwarranted-praise-of-russia/}{``The world is right to be concerned by Donald Trump's unwarranted praise of Russia''} (2017)}
			\subentry{\href{http://blogs.lse.ac.uk/government/2016/01/14/what-can-social-scientists-learn-from-convenience-samples-more-than-you-might-think/}{``What can social scientists learn from convenience samples? More than you might think''} (2015)}
		\entry{LSE US Politics and Policy Blog}
			\subentry{\href{http://blogs.lse.ac.uk/usappblog/2016/11/10/trump-owes-his-victory-to-americas-unique-electoral-college-system/}{``Trump owes his victory to America's unique Electoral College system''} (2016)}
			\subentry{\href{http://blogs.lse.ac.uk/usappblog/2016/10/05/vice-presidents-are-a-heartbeat-from-the-oval-office-but-matter-very-little/}{``Vice Presidents are a heartbeat from the Oval Office, but matter very little''} (2016)}
			\subentry{\href{http://blogs.lse.ac.uk/usappblog/2016/09/23/for-voters-the-2016-election-campaign-is-a-marathon-with-very-limited-choices/}{``For voters, the 2016 election campaign is a marathon with very limited choices''} (2016)}
		\entry{LSE British Politics and Policy Blog}
			\subentry{\href{http://blogs.lse.ac.uk/politicsandpolicy/non-eu-migration-is-what-uk-voters-care-most-about/}{``UK voters, including Leavers, care more about reducing non-EU than EU migration''} (2017)}
        \entry{LSE European Politics and Policy Blog}
			\subentry{\href{http://blogs.lse.ac.uk/europpblog/2017/06/07/uk-general-election-preview-what-to-look-out-for-as-britain-goes-to-the-polls/}{``The Brexit election that never was.''} (2017)}
            \subentry{\href{http://blogs.lse.ac.uk/europpblog/2016/06/23/voters-listen-people-like-them/}{``Voters might be fed up with politicians, but they will listen to people `like them' ''} (2016)}
		\entry{LSE Social Science Impact Blog}
			\subentry{\href{http://blogs.lse.ac.uk/impactofsocialsciences/2016/05/18/elsevier-purchase-ssrn-social-scientists-face-questions-over-whether-centralised-repository-is-in-their-interests/}{``Elsevier purchase SSRN: Social scientists face questions over whether centralised repository is in their interests''} (2016)}
		\entry{The New West}
			\subentry{\href{https://thewpsa.wordpress.com/2015/05/09/what-can-we-learn-from-10-1-million-facebook-users-its-complicated/}{``What Can We Learn from 10.1 Million Facebook Users? `It's Complicated'.''} (2015)}
		\entry{The Political Methodologist}
			\subentry{\href{https://thepoliticalmethodologist.com/2013/11/25/making-high-resolution-graphics-for-academic-publishing/}{``Making High-Resolution Graphics for Academic Publishing''} (2013) -- \href{http://thepoliticalmethodologist.com/2015/01/05/introducing-the-annual-tpm-most-viewed-post-award-and-our-2014-winner/}{\textit{The Political Methodologist}'s Most Viewed Post of 2014}}
		\entry{\href{http://ropensci.org/blog/}{rOpenSci} (2014)}
			\subentry{\href{https://ropensci.org/blog/2017/04/18/tabulizer/}{``Release `open' data from their PDF prisons using tabulizer''} (2017)}
            \subentry{\href{https://ropensci.org/blog/2014/02/20/dvn-dataverse-network/}{``Sharing Reproducible Research from R''} (2014)}
		\entry{\href{http://politicalsciencereplication.wordpress.com/}{PoliSci Replication} (2014)}
			\subentry{\href{https://politicalsciencereplication.wordpress.com/2014/06/04/guest-post-be-a-better-scientist-how-to-make-your-scientific-output-more-credible-by-thomas-leeper/}{``Be a Better Scientist -- How to Make Your Scientific Output More Credible''} (2014)}
			\subentry{\href{https://politicalsciencereplication.wordpress.com/2014/05/21/guest-post-why-reproducibility-requires-data-archiving-by-thomas-leeper/}{``Archive Your Data or They Die With You''} (2014)}
		\entry{``\href{http://www.psychologytoday.com/blog/polarized}{Polarized},'' a \textit{Psychology Today} blog about psychology and public opinion (2012-2013)}
	
	\topic{Public and non-academic presentations}
		\subentry{American Politics Q\&A for cast and crew of production of Gore Vidal's \textit{The Best Man} (2017)}
        \subentry{Panelist, LSE Student Union Women in Politics Society Event (2016)}
        \subentry{Panelist, LSE Student Union Hong Kong Public Affairs and Social Science Society Event (2016)}

	\topic{Miscellaneous}
		\entry{Assistance with statistics, R programming, and Amazon Mechanical Turk on \href{http://stackoverflow.com/users/2338862/thomas}{StackOverflow}. (2013--present; ``trusted user'' 2015--present)}

\end{document}
